Summary Outcome Tables

### 2020-07-31 summary_tables_outcomes.Rmd
Add sections for cities and their WHW matrices
Add table headers

```{r whw}

@@

for(city in cities){
  # if (!city %in% c('buenos_aires', 'mexico_city'))
  {
    # city <- 'buenos_aires'
    for (cs in names(io$accra$outcomes$whw)){
      print(city)

@@

@@

      ft <- flextable(temp)
      cat(knit_print(ft))

@@

### Who hit whom matrix for all case cities {#whw_all}

@@

scen_names <- unique(whw_list$scenario)
for (i in 1:length(scen_names)){
  sn <- scen_names[i]
  cat('###', sn, ' scenario', '\n')

@@

    index <- index + 1
    cat('\n')
    cat('####', cm, '\n')
    #print(kable(format(temp1, scientific = F), caption = paste('Who Hit Whom (WHW) for ', scen_names[i], 'scenario and ', cas_mode[j], ' mode')))

>>>>

```{r whw, results = 'asis', fig.width=7, fig.height=4, echo=FALSE}

@@

for(city in cities){
  {
    cat('\n')

    cat('###', city, '\n')

    for (cs in names(io$accra$outcomes$whw)){

@@

      cat('####', qualified_scen_name, ' WHW', '\n')

@@

      ft <- flextable(temp)
      ft <- add_header_row(ft, values = c('Strike Mode', 'Casualty Mode'), colwidths = c(1, ncol(temp) - 1))

      #ft <- autofit(ft)
      cat(knit_print(ft))

@@

## Who hit whom matrix for all case cities {#whw_all}

@@

scen_names <- unique(whw_list$scenario)
for (i in 1:length(scen_names)){
  sn <- scen_names[i]
  cat('##', sn, ' scenario', '\n')

@@

    index <- index + 1
    cat('\n')
    cat('###', cm, '\n')
    #print(kable(format(temp1, scientific = F), caption = paste('Who Hit Whom (WHW) for ', scen_names[i], 'scenario and ', cas_mode[j], ' mode')))
